---
title: "Able.com Case Study"
author: "Anais Corral"
date: "2024-08-24"
output:
  html_document:
    toc: true
    toc_depth: 3 
  pdf_document: default
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
```

# Load data & preparation

```{r}
# Importing observed toy sales data

toy_sales <- read.csv("https://raw.githubusercontent.com/jefftwebb/data/main/toy_sales_data.csv")

# Importing toy sales data with potential outcomes 
toy_sales_PO <- read.csv(url("https://raw.githubusercontent.com/jefftwebb/data/main/toy_sales_PO.csv"))

head(toy_sales)
head(toy_sales_PO)
```

# Question 1

```{r}
# Calculate the true ATE
ATE <- mean(toy_sales_PO$y1 - toy_sales_PO$y0)
ATE
```

45.9 means that, on average, stores sold about 46 more units when they
had a sale compared to when they didn't.

# Question 2

```{r}
# Calculate the average sales for weeks with a sale
avg_sales_with_sale <- mean(toy_sales$weekly_amount_sold[toy_sales$is_on_sale == 1])

# Calculate the average sales for weeks without a sale
avg_sales_without_sale <- mean(toy_sales$weekly_amount_sold[toy_sales$is_on_sale == 0])

# Calculate the estimated ATE
estimated_ATE <- avg_sales_with_sale - avg_sales_without_sale
estimated_ATE

```

The observed data suggests that stores sell about 78 more units during a
sale, but the true impact is actually closer to 46 units. This means the
observed data might be overestimating the effect of having a sale.

# Question 3

The bias in using observed data to estimate the ATE comes from other
factors that might influence sales during sale weeks. These factors
could cause the observed effect to seem larger than the true impact of
the sale, leading to an overestimation of the sale's actual effect.

# Question 4

```{r}
# Creating a balance table

# Calculate mean and standard deviation of avg_week_sales for treatment and control groups
mean_with_sale <- mean(toy_sales$avg_week_sales[toy_sales$is_on_sale == 1])
sd_with_sale <- sd(toy_sales$avg_week_sales[toy_sales$is_on_sale == 1])

mean_without_sale <- mean(toy_sales$avg_week_sales[toy_sales$is_on_sale == 0])
sd_without_sale <- sd(toy_sales$avg_week_sales[toy_sales$is_on_sale == 0])

# Create a balance table
balance_table <- data.frame(
  Group = c("With Sale", "Without Sale"),
  Mean_avg_week_sales = c(mean_with_sale, mean_without_sale),
  SD_avg_week_sales = c(sd_with_sale, sd_without_sale)
)

balance_table

```

The balance table shows that stores with sales have higher average
weekly sales and more variability compared to those without sales. This
indicates that the two groups aren't fully comparable, suggesting
potential bias in estimating the effect of having a sale.

The groups aren't fully exchangeable because stores with sales generally
sell more each week than those without sales. This difference suggests
that the stores running sales might be bigger or more successful, making
it hard to compare the two groups fairly. As a result, it's difficult to
say that any increase in sales is only due to the sale itself, because
other factors might be at play.

# Question 5

```{r}
# Fit a linear regression model adjusting for avg_week_sales
model <- lm(weekly_amount_sold ~ is_on_sale + avg_week_sales, data = toy_sales)

# Summary of the model
summary(model)

# Extract the coefficient for is_on_sale, which represents the adjusted ATE
adjusted_ATE <- coef(model)["is_on_sale"]
adjusted_ATE

```

## Report an adjusted ATE

The adjusted ATE is 69 units, which is closer to the true ATE of 46
units, but still slightly higher.

## How does it compare to the true ATE?

The adjustment accounts for company size, helping to reduce bias by
considering that larger stores typically sell more, making the ATE
estimate more accurate.

The adjusted ATE of 69 units, while closer to the true ATE of 46 units,
suggests that accounting for company size reduces the overestimation
seen in the unadjusted analysis. This adjustment is important because it
controls for the fact that larger stores, which tend to sell more
products, are more likely to run sales. By considering company size, the
model provides a more realistic estimate of the sale's impact, although
it still slightly overestimates the true effect, indicating that there
may be other factors at play that were not accounted for in the model.

# Question 6

```{r}
# Load the toy_sales_PO.csv data (assuming already loaded as toy_sales_PO)

# Calculate CATE for each level of weeks_to_xmas
cate_3 <- mean(toy_sales_PO$y1[toy_sales_PO$weeks_to_xmas == 3] - toy_sales_PO$y0[toy_sales_PO$weeks_to_xmas == 3])
cate_2 <- mean(toy_sales_PO$y1[toy_sales_PO$weeks_to_xmas == 2] - toy_sales_PO$y0[toy_sales_PO$weeks_to_xmas == 2])
cate_1 <- mean(toy_sales_PO$y1[toy_sales_PO$weeks_to_xmas == 1] - toy_sales_PO$y0[toy_sales_PO$weeks_to_xmas == 1])
cate_0 <- mean(toy_sales_PO$y1[toy_sales_PO$weeks_to_xmas == 0] - toy_sales_PO$y0[toy_sales_PO$weeks_to_xmas == 0])

# Print the results
cate_3
cate_2
cate_1
cate_0

```

CATE for Weeks to Christmas = 3: 49.78 units CATE for Weeks to Christmas
= 2: 48.94 units CATE for Weeks to Christmas = 1: 46.14 units CATE for
Weeks to Christmas = 0: 38.75 units

The impact of running a sale gets smaller as Christmas gets closer.
Sales have a bigger effect 3 weeks before Christmas than they do in the
final week, suggesting that shoppers may be more influenced by sales
earlier in the month.

# Question 7

```{r}
# Fit the linear regression model with an interaction term between is_on_sale and weeks_to_xmas
model_interaction <- lm(weekly_amount_sold ~ is_on_sale * weeks_to_xmas + avg_week_sales, data = toy_sales)

# Summary of the model (if you want to check the coefficients)
summary(model_interaction)

# Coefficients from the model
coefficients <- coef(model_interaction)

# Calculate adjusted CATE for each level of weeks_to_xmas
cate_adjusted_3 <- coefficients["is_on_sale"] + coefficients["is_on_sale:weeks_to_xmas"] * 3
cate_adjusted_2 <- coefficients["is_on_sale"] + coefficients["is_on_sale:weeks_to_xmas"] * 2
cate_adjusted_1 <- coefficients["is_on_sale"] + coefficients["is_on_sale:weeks_to_xmas"] * 1
cate_adjusted_0 <- coefficients["is_on_sale"]

# Create a data frame for comparison
comparison <- data.frame(
  Weeks_to_Xmas = c(3, 2, 1, 0),
  True_CATE = c(49.78, 48.94, 46.14, 38.75),
  Adjusted_CATE = c(cate_adjusted_3, cate_adjusted_2, cate_adjusted_1, cate_adjusted_0)
)

# Print the comparison table to check the values
print(comparison)
```

```{r}
# Plotting the comparison between True CATE and Adjusted CATE
library(ggplot2)

ggplot(comparison, aes(x = factor(Weeks_to_Xmas))) +
  geom_bar(aes(y = True_CATE, fill = "True CATE"), stat = "identity", position = "dodge", width = 0.4) +
  geom_bar(aes(y = Adjusted_CATE, fill = "Adjusted CATE"), stat = "identity", position = "dodge", width = 0.4) +
  labs(x = "Weeks to Christmas", y = "CATE (Units Sold)", title = "Comparison of True CATE vs. Adjusted CATE") +
  scale_fill_manual(values = c("True CATE" = "blue", "Adjusted CATE" = "red")) +
  theme_minimal()
```

## CATE for Weeks to Christmas = 3: - True CATE: 49.78 units - Adjusted

CATE: 65.27 units - Comment: The adjusted CATE is higher than the true
CATE by about 15.49 units.

## CATE for Weeks to Christmas = 2: - True CATE: 48.94 units - Adjusted

CATE: 55.78 units - Comment: The adjusted CATE is higher than the true
CATE by about 6.84 units.

## CATE for Weeks to Christmas = 1: - True CATE: 46.14 units - Adjusted

CATE: 46.29 units - Comment: The adjusted CATE is very close to the true
CATE, differing by only 0.15 units.

## CATE for Weeks to Christmas = 0: - True CATE: 38.75 units - Adjusted

CATE: 37.80 units - Comment: The adjusted CATE is slightly lower than
the true CATE by about 0.95 units.

The adjusted CATEs are generally higher than the true CATEs for weeks 2
and 3, indicating that the model may overestimate the effect of the sale
as Christmas approaches. However, for weeks 1 and 0, the adjusted CATEs
are very close to the true CATEs, suggesting that the model captures the
impact of the sale more accurately as the event draws nearer. Overall,
the model seems to reflect the increasing urgency of shoppers but might
slightly overstate the effect of sales in the weeks further out from
Christmas.
